---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

The GitHub repository also contains the dataset for the assignment so you do not have to download the data separately.

### Loading data

So we just unzip it and read into the data frame
```{r}
unzip(zipfile = "activity.zip", files = "activity.csv")
data <- read.csv(file = "activity.csv", na.strings = "NA")
```

Let's make some assertions
```{r}
assertthat::are_equal(nrow(data), 17568) # As given in task
assertthat::are_equal(ncol(data), 3) # As given in task
```

Let's have a look at the data
```{r}
colnames(data)
head(data)
tail(data)
```

### Process/transform the data (if necessary) into a format suitable for your analysis

```{r}
data = transform(data, date = as.Date(date))

library(data.table)

datt <- data.table(data)
```

## What is mean total number of steps taken per day?

Missing values are ignored.

### Make a histogram of the total number of steps taken each day
```{r}
sum_by_days <- datt[, sum(steps, na.rm = TRUE), by = date]$V1
hist(sum_by_days,
     main = "Histogram of the total number of steps taken each day",
     xlab = "Sum of steps by days",
     ylab = "Frequency")
```

### Calculate and report the mean and median total number of steps taken per day
```{r}
mean(sum_by_days)
median(sum_by_days)
```

## What is the average daily activity pattern?



    Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

    Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?




## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
